Advancements in Moltres for Time-Dependent Multiphysics Molten Salt Reactor Modeling

### 2024-12-05 presentation/3d-transient.tex
slide edits

\begin{frame}
  \frametitle{Time-Dependent Multiphysics Simulations with the Hybrid Method}
  I investigated two transient scenarios based on actual MSRE experiments:
  \begin{block}{\textbf{MSRE Rod Drop Experiment}}
    \begin{itemize}
      \item Neutronic response of an initially critical, zero-power MSRE to a
        rod drop of Rod 1 \cite{prince_zero-power_1968}
      \item Corresponds to a reactivity withdrawal of -1500 pcm
      \item Requires delayed neutron precursor (DNP) modeling
    \end{itemize}
  \end{block}
  \begin{block}{\textbf{MSRE Reactivity Insertion Experiment}}
    \begin{itemize}
      \item Coupled power response of the MSRE initially at 1 MW to a rod
        withdrawal \cite{engel_zero-power_1972}
      \item Reactivity insertion of 24.8 pcm
      \item MSRE fueled with $^{233}$U
      \item Requires DNP and temperature advection-diffusion modeling
    \end{itemize}
  \end{block}
\end{frame}

@@

\begin{frame}
  \frametitle{MSRE Rod Drop Experiment}
  \textbf{Integral Neutron Count Following Rod Drop}
  \begin{figure}[t]
    \centering
    \includegraphics[width=0.55\columnwidth]{integral-count}
    \caption{Integral neutron count during the rod drop experiment from \gls{MSRE} experimental data
    and hybrid method numerical results.}
    \label{fig:integral-count}
  \end{figure}
  \begin{itemize}
    \item Moltres underpredicted the integral neutron count rate by approximately 20 \%.
    \item Potential sources of error
    \begin{itemize}
      \item Uncertainty in the initial neutron count rate
      \item Miscalculation of -1500 pcm reactivity withdrawal
    \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{MSRE Reactivity Insertion Experiment}
  \textbf{Nested Coupling Iteration Structure for the Reactivity Insertion Simulation}
  \begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{images/nest-2}
    \caption{The nested iteration structure coupling the $S_N$, neutron diffusion,
    in-core \gls{DNP}-temperature, and ex-core
    solvers for the reactivity insertion simulation using the hybrid $S_N$-diffusion method.}
    \label{fig:insertion-coupling}
  \end{figure}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Time-Dependent Simulations with the Hybrid Method}
%  I investigated two transient scenarios based on actual MSRE experiments:
  Time-dependent reactivity-initiated simulation based on an MSRE rod drop experiment.
  \begin{block}{\textbf{MSRE Rod Drop Experiment}}
    \begin{itemize}
      \item Neutronic response of an initially critical, zero-power MSRE to a
        rod drop of Rod 1 \cite{prince_zero-power_1968}
      \item Corresponds to a reactivity withdrawal of -1500 pcm
      \item Requires delayed neutron precursor (DNP) modeling
      \item Induces a prompt response, followed by a delayed response, in the neutron count rate
    \end{itemize}
  \end{block}
%  \begin{block}{\textbf{MSRE Reactivity Insertion Experiment}}
%    \begin{itemize}
%      \item Coupled power response of the MSRE initially at 1 MW to a rod
%        withdrawal \cite{engel_zero-power_1972}
%      \item Reactivity insertion of 24.8 pcm
%      \item MSRE fueled with $^{233}$U
%      \item Requires DNP and temperature advection-diffusion modeling
%    \end{itemize}
%  \end{block}
\end{frame}

@@

\begin{frame}
  \frametitle{MSRE Rod Drop Experiment}
  \textbf{Neutron Count Rate Following Rod Drop}
  \begin{columns}
    \column{5.5cm}
    \begin{figure}[t]
      \centering
      \includegraphics[width=\columnwidth]{count-rate}
      \caption{Neutron count rate during the rod drop experiment from Moltres rod drop simulation.}
      \label{fig:count-rate}
    \end{figure}
    \column{5.5cm}
    \begin{itemize}
      \item Steep initial decline in neutron count rate as the rod drops
      \item Decline in neutron count rate slows at $t=0.5$ s due to presence of DNPs
      \item Convergence issues prevented the simulation from converging from $t = 0.8$ s
      \item I raised the convergence tolerance to help the simulation continue
    \end{itemize}
  \end{columns}
%  \begin{itemize}
%    \item Moltres underpredicted the integral neutron count rate by approximately 20 \%.
%    \item Potential sources of error
%    \begin{itemize}
%      \item Uncertainty in the initial neutron count rate
%      \item Miscalculation of -1500 pcm reactivity withdrawal
%    \end{itemize}
%  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{MSRE Rod Drop Experiment}
  \textbf{Integral Neutron Count Following Rod Drop}
  \begin{columns}
    \column{5.5cm}
    \begin{figure}[t]
      \centering
      \includegraphics[width=\columnwidth]{integral-count}
      \caption{Integral neutron count during the rod drop experiment from \gls{MSRE} experimental data
      and hybrid method numerical results.}
      \label{fig:integral-count}
    \end{figure}
    \column{5.5cm}
    \begin{itemize}
      \item Moltres reproduces the expected trend in the integral neutron count rate
      \item Slight underprediction relative to MSRE rod drop experimental data
      \item Underprediction may be due to experimental uncertainty in $^{235}$U concentration,
        initial \& final rod height, initial neutron count rate.
    \end{itemize}
  \end{columns}
%  \begin{itemize}
%    \item Moltres underpredicted the integral neutron count rate by approximately 20 \%.
%    \item Potential sources of error
%    \begin{itemize}
%      \item Uncertainty in the initial neutron count rate
%      \item Miscalculation of -1500 pcm reactivity withdrawal
%    \end{itemize}
%  \end{itemize}
\end{frame}

%\begin{frame}
%  \frametitle{MSRE Reactivity Insertion Experiment}
%  \textbf{Nested Coupling Iteration Structure for the Reactivity Insertion Simulation}
%  \begin{figure}[t]
%    \centering
%    \includegraphics[width=\columnwidth]{images/nest-2}
%    \caption{The nested iteration structure coupling the $S_N$, neutron diffusion,
%    in-core \gls{DNP}-temperature, and ex-core
%    solvers for the reactivity insertion simulation using the hybrid $S_N$-diffusion method.}
%    \label{fig:insertion-coupling}
%  \end{figure}
%\end{frame}

\begin{frame}
  \frametitle{3-D Modeling with the Hybrid Method}
  \begin{block}{\textbf{Difficulties Faced During 3-D Modeling}}
  \begin{itemize}
    \item Poor convergence rate relative to 1-D \& 2-D modeling
    \begin{itemize}
      \item Likely due to increased streaming effects in 3-D near-void (air) regions in the reactor
    \end{itemize}
    \item Significant memory requirements
    \item Lagged control rod positions in fixed point iterations affecting convergence in time-dependent
      simulations $\Rightarrow$ simulation requires smaller timestep sizes
  \end{itemize}
\end{block}
\end{frame}

### 2024-12-05 presentation/future.tex
slide edits

\begin{frame}
  \begin{block}{\textbf{Future Work}}
    \begin{itemize}
      \item Extend the Spalart-Allmaras turbulence model implementation
      \begin{itemize}
        \item Investigate more effective preconditioning schemes beyond the
          current additive Schwarz method
        \item Implement wall functions to reduce fine mesh requirements near the wall for high
          Reynolds flows (Re$\approx 10^6$)
      \end{itemize}
      \item Improve the computational performance of the hybrid $S_N$-diffusion method
      \begin{itemize}
        \item General code optimizations
        \item Reduce compute and memory use through shared FEM Jacobian evaluations for all angular
          fluxes at the same position
        \item Custom mesh distribution and data transfer caching routines to minimize data transfer time
      \end{itemize}
      \item Further 3-D full-core reactor analyses with the hybrid method
      \begin{itemize}
        \item Other MSRs designs with control rods include the Chinese TMSR-LF1,
          Terrapower's MCRE, and the Seaborg Technology's CMSR
        \item These reactor designs allow for asymmetric reactivity-initiated transients due to
          non-centrally located control rods.
      \end{itemize}
    \end{itemize}
  \end{block}
\end{frame}

>>>>

\begin{frame}
  \begin{block}{\textbf{Future Work}}
    \textbf{Extend the Spalart-Allmaras turbulence model implementation}
      \begin{itemize}
        \item Investigate more effective preconditioning schemes beyond the
          current additive Schwarz method
        \item Implement wall functions to reduce fine mesh requirements near the wall for high
          Reynolds flows (Re$\approx 10^6$)
      \end{itemize}
    \textbf{Improve the computational performance of the hybrid $S_N$-diffusion method}
      \begin{itemize}
        \item General code optimizations
        \item Reduce compute and memory use through shared FEM Jacobian evaluations for all angular
          fluxes at the same position
        \item Custom mesh distribution and data transfer caching routines to minimize data transfer time
        \item Preconditioning method or other optimizations to improve convergence of modified neutron diffusion
          method
      \end{itemize}
    \textbf{Further 3-D full-core reactor analyses with the hybrid method}
      \begin{itemize}
        \item Other MSRs designs with control rods include the Chinese TMSR-LF1,
          Terrapower's MCRE, and the Seaborg Technology's CMSR
        \item These reactor designs allow for asymmetric reactivity-initiated transients due to
          non-centrally located control rods.
      \end{itemize}
  \end{block}
\end{frame}

### 2024-12-05 presentation/msre-transients.tex
slide edits

\begin{frame}
  \frametitle{V\&V Study 2: MSRE Pump Start-up \& Coast-Down Transients}
  \textbf{Description of MSRE Pump Experiments}
  \begin{itemize}
    \item Pump start-up and coast-down transient flow-rate tests on the MSRE under zero-power
  conditions
    \item Starting from zero-power critical states with/without forced flow, the fuel salt pump
  was coasted down/started up
    \item Reactor was kept critical by a flux-servo controller moving the rod in response to flux
      changes
  \end{itemize}
  \begin{columns}
    \column[t]{5.5cm}
    \begin{figure}
      \centering
      \includegraphics[width=.8\columnwidth]{images/msre-startup}
      \caption{MSRE start-up pump speed and flow rate experimental data
      \cite{prince_zero-power_1968}.}
    \end{figure}
    \column[t]{5.5cm}
    \begin{figure}
      \centering
      \includegraphics[width=.95\columnwidth]{images/msre-coastdown}
      \caption{MSRE coast-down pump speed and flow rate experimental data
      \cite{prince_zero-power_1968}.}
    \end{figure}
  \end{columns}
\end{frame}

@@

\begin{frame}
  \frametitle{V\&V Study 2: MSRE Pump Start-up \& Coast-Down Transients}
  \begin{columns}
    \column{6.5cm}
    \begin{block}{\textbf{MSR Phenomena Involved}}
      \begin{itemize}
        \item DNP drift under time-varying flow
        \item Loss of delayed neutrons due to out-of-core DNP decay
      \end{itemize}
    \end{block}
    \begin{block}{\textbf{Aim of the Study}}
      \begin{itemize}
         \item Develop a V\&V study based on the MSRE pump start-up \& coast-down
           transients that is easily reproducible
         \item Verify Moltres against QuasiMolto in collaboration with Aaron Reynolds
           (formerly at Oregon State University)
         \item Validate Moltres against MSRE experimental data for modeling \gls{DNP} drift
       \end{itemize}
    \end{block}
    \begin{block}{\textbf{Modeling Approach}}
      \begin{itemize}
        \item Two neutron energy groups and six DNP groups
        \item Group constants generated using a representative unit cell model in SCALE
        \item Ignored upper and lower plena in the geometry
        \item Looped salt flow with a salt circulation time of 25.2 s
        \item $k$-eigenvalue calculation at every time-step in place of reactivity control
        \item Timestep size of 0.1 s
      \end{itemize}
    \end{block}
    \column{4.5cm}
    \begin{figure}[htb]
      \centering
      \includegraphics[width=0.8\columnwidth]{images/msre-2d}
      \caption{2-D axisymmetric model of the \gls{MSRE}.The gray and white regions represent fuel salt
      and graphite, respectively. Fuel salt channels are 1.25-cm wide and spaced at 5-cm intervals.}
      \label{fig:pump-geom}
    \end{figure}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{V\&V Study 2: MSRE Pump Start-up \& Coast-Down Transients}
  \textbf{Static \& Steady-Flow Conditions}
  \begin{table}[htb]
    \centering
    \caption{Multiplication factors $k_\text{eff}$ under static and steady salt flow conditions, and
    reactivity changes $\Delta\rho$ due to \gls{DNP} flow from the Moltres and QuasiMolto \gls{MSRE}
    models.}
    \begin{tabular}{l S S S}
      \toprule
      \multirow{2}{*}{Code} & \multicolumn{2}{c}{$k_\text{eff}$} & {$\Delta\rho$ due to} \\
                            & {Static} & {Steady flow} & {\gls{DNP} flow} \\
                            \cmidrule(r){1-1} \cmidrule(rl){2-3} \cmidrule(l){4-4}
      Moltres & 1.05625 & 1.05311 & -282.4 \\
      QuasiMolto & 1.05603 & 1.05290 & -281.7 \\
      \bottomrule
    \end{tabular}
    \label{table:msre-pump-keff}
  \end{table}

  \begin{itemize}
    \item Excellent agreement between Moltres and QuasiMolto under static and steady-flow conditions prior
  to the pump transients.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{V\&V Study 2: MSRE Pump Start-up \& Coast-Down Transients}
  \textbf{Neutron Flux Distributions Under Static Conditions}
  \begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{centerline_flux}
      \caption{Normalized centerline neutron fluxes.}
      \label{fig:centerline-flux-dist}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{midplane_flux}
      \caption{Normalized midplane neutron fluxes.}
      \label{fig:midplane-flux-dist}
    \end{subfigure}
    \caption{Neutron flux distributions comparing QuasiMolto and Moltres
    \gls{MSRE} models under static conditions. Maximum relative difference $\approx 0.8 \%$.}
    \label{fig:centerline-flux}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{V\&V Study 2: MSRE Pump Start-up \& Coast-Down Transients}
  \textbf{DNP Distributions Under Static Conditions}
  \begin{figure}[t]
    \centering
    \begin{subfigure}[b]{0.48\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{centerline_pre}
      \caption{Normalized centerline \gls{DNP} distributions.}
      \label{fig:centerline-pre-dist}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{midplane_pre}
      \caption{Normalized midplane \gls{DNP} distributions.}
      \label{fig:midplane-pre-dist}
    \end{subfigure}
    \caption{\gls{DNP} distribution from Moltres and ratios comparing QuasiMolto and
    Moltres models under static \gls{MSRE} conditions. Maximum relative difference $\approx 0.1 \%$.}
    \label{fig:centerline-pre}
  \end{figure}
\end{frame}

@@

\begin{frame}
  \frametitle{V\&V Study 2: MSRE Pump Start-up \& Coast-Down Transients}
  \textbf{Study Outcome}
  \begin{itemize}
    \item Moltres and QuasiMolto are highly consistent with each other in their looped DNP flow
      modeling capabilities
    \item Moltres and QuasiMolto reproduced key reactivity behavior in response to varying salt
      flow velocities
    \item Some discrepancies observed between the numerical and experimental results due to the
      omission of upper and lower plena
    \item This study can be used for verifying advection capabilities in other MSR simulation tools
    \item The distinct oscillations serve as valuable reference points to facilitate code-to-code
      comparisons
  \end{itemize}
\end{frame}

>>>>

\begin{frame}
  \frametitle{V\&V Study 2: MSRE Pump Start-up \& Coast-Down Transients}
  \textbf{Description of MSRE Pump Experiments}
  \begin{itemize}
    \item Starting from zero-power critical states with/without forced flow, the fuel salt pump
  was coasted down/started up
    \item Reactor was kept critical by a flux-servo controller moving the rod in response to flux
      changes
  \end{itemize}
  \begin{block}{\textbf{MSR Phenomena Involved}}
    \begin{itemize}
      \item DNP drift under time-varying flow
      \item Loss of delayed neutrons due to out-of-core DNP decay
    \end{itemize}
  \end{block}
  \begin{columns}
    \column{5.5cm}
    \begin{figure}
      \centering
      \includegraphics[width=.8\columnwidth]{images/msre-startup}
      \caption{MSRE start-up pump speed and flow rate experimental data
      \cite{prince_zero-power_1968}.}
    \end{figure}
    \column{5.5cm}
    \begin{figure}
      \centering
      \includegraphics[width=.95\columnwidth]{images/msre-coastdown}
      \caption{MSRE coast-down pump speed and flow rate experimental data
      \cite{prince_zero-power_1968}.}
    \end{figure}
  \end{columns}
\end{frame}

@@

\begin{frame}
  \frametitle{V\&V Study 2: MSRE Pump Start-up \& Coast-Down Transients}
  \begin{columns}
    \column{6.5cm}
    \begin{block}{\textbf{Aim of the Study}}
      \begin{itemize}
         \item Develop a V\&V study based on the MSRE pump transients
         \item Verify Moltres against QuasiMolto in collaboration with Aaron Reynolds
           (formerly at Oregon State University)
         \item Validate Moltres against MSRE experimental data for modeling \gls{DNP} drift
       \end{itemize}
    \end{block}
    \begin{block}{\textbf{Modeling Approach}}
      \begin{itemize}
        \item Two neutron energy groups and six DNP groups
        \item Ignored upper and lower plena in the geometry
        \item Looped salt flow with a salt circulation time of 25.2 s
        \item $k$-eigenvalue calculation at every time-step ($dt=0.1$ s) in place of reactivity control
      \end{itemize}
    \end{block}
    \column{4.5cm}
    \begin{figure}[htb]
      \centering
      \includegraphics[width=0.8\columnwidth]{images/msre-2d}
      \caption{2-D axisymmetric model of the \gls{MSRE}.The gray and white regions represent fuel salt
      and graphite, respectively. Fuel salt channels are 1.25-cm wide and spaced at 5-cm intervals.}
      \label{fig:pump-geom}
    \end{figure}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{V\&V Study 2: MSRE Pump Start-up \& Coast-Down Transients}
  \textbf{$k_\text{eff}$ Under Static \& Steady-Flow Conditions}
  \begin{table}[htb]
    \centering
    \caption{Multiplication factors $k_\text{eff}$ under static and steady salt flow conditions, and
    reactivity changes $\Delta\rho$ due to \gls{DNP} flow from the Moltres and QuasiMolto \gls{MSRE}
    models.}
    \begin{tabular}{l S S S}
      \toprule
      \multirow{2}{*}{Code} & \multicolumn{2}{c}{$k_\text{eff}$} & {$\Delta\rho$ due to} \\
                            & {Static} & {Steady flow} & {\gls{DNP} flow} \\
                            \cmidrule(r){1-1} \cmidrule(rl){2-3} \cmidrule(l){4-4}
      Moltres & 1.05625 & 1.05311 & -282.4 \\
      QuasiMolto & 1.05603 & 1.05290 & -281.7 \\
      \bottomrule
    \end{tabular}
    \label{table:msre-pump-keff}
  \end{table}
  \begin{itemize}
    \item Excellent agreement between Moltres and QuasiMolto under static and steady-flow conditions prior
  to the pump transients.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{V\&V Study 2: MSRE Pump Start-up \& Coast-Down Transients}
  \textbf{Neutron Flux Distributions Under Static Conditions}
  \begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{centerline_flux}
      \caption{Normalized centerline neutron fluxes.}
      \label{fig:centerline-flux-dist}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{midplane_flux}
      \caption{Normalized midplane neutron fluxes.}
      \label{fig:midplane-flux-dist}
    \end{subfigure}
    \caption{Neutron flux distributions comparing QuasiMolto and Moltres
    \gls{MSRE} models under static conditions. Maximum relative difference $\approx 0.8 \%$.}
    \label{fig:centerline-flux}
  \end{figure}
  \begin{itemize}
    \item Perfect overlap in centerline and midplane neutron fluxes between Moltres and QuasiMolto.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{V\&V Study 2: MSRE Pump Start-up \& Coast-Down Transients}
  \textbf{DNP Distributions Under Static Conditions}
  \begin{figure}[t]
    \centering
    \begin{subfigure}[b]{0.48\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{centerline_pre}
      \caption{Normalized centerline \gls{DNP} distributions.}
      \label{fig:centerline-pre-dist}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{midplane_pre}
      \caption{Normalized midplane \gls{DNP} distributions.}
      \label{fig:midplane-pre-dist}
    \end{subfigure}
    \caption{\gls{DNP} distribution from Moltres and ratios comparing QuasiMolto and
    Moltres models under static \gls{MSRE} conditions. Maximum relative difference $\approx 0.1 \%$.}
    \label{fig:centerline-pre}
  \end{figure}
  \begin{itemize}
    \item Perfect overlap in centerline and midplane DNP distributions between Moltres and QuasiMolto.
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{V\&V Study 2: MSRE Pump Start-up \& Coast-Down Transients}
  \begin{block}{\textbf{Study Outcome}}
    \begin{itemize}
      \item Moltres and QuasiMolto are highly consistent with each other in their looped DNP flow
        modeling capabilities
      \item Moltres and QuasiMolto reproduced key reactivity behavior in response to varying salt
        flow velocities
      \item Some discrepancies observed between the numerical and experimental results due to the
        omission of upper and lower plena
      \item This study can be used for verifying advection capabilities in other MSR simulation tools
      \item The distinct oscillations serve as valuable reference points to facilitate code-to-code
        comparisons
    \end{itemize}
  \end{block}
\end{frame}

### 2024-12-05 presentation/review.tex
slide edits

  Gol'din originally developed the quasi-diffusion (QD) method as a transport method acceleration
  scheme \cite{goldin_quasi-diffusion_1964}.
  \begin{gather}
    \mbox{\small Zeroth angular moment: } 
    \nabla\cdot J(\vec{r}) + \Sigma_t(\vec{r})\phi(\vec{r}) = \Sigma_{s,0}(\vec{r})\phi(\vec{r}) +
    Q_0(\vec{r}) \label{eq:qd-low-0th} \\
    \mbox{\small First angular moment: }
    \nabla\cdot\left(\vec{\vec{E}}(\vec{r})\phi(\vec{r})\right) + \Sigma_t(\vec{r})J(\vec{r}) =
    \Sigma_{s,1}(\vec{r})J(\vec{r}) + Q_1(\vec{r}) \label{eq:qd-low-1st}
    \shortintertext{\small where}
    \vec{\vec{E}} = \frac{\int_{4\pi}d\hat{\Omega}\ \hat{\Omega}\hat{\Omega}\psi(\vec{r})}{
    \int_{4\pi}d\hat{\Omega}\ \psi(\vec{r})} = \mbox{\small Eddington tensor}.
  \end{gather}
  %
  Gol'din later extended it to a three-level method by deriving effective gray (one-group)
  low-order QD equations \cite{anistratov_solution_1986}.
\end{frame}

@@

  It uses two-level neutronics method based on the Second-Moment method. The low-order
  second-moment equations at the $(s+1)$th iteration are:
  \begin{gather}
    \nabla\cdot J^{(s+1)}+\Sigma_a\phi^{(s+1)} = q, \label{eq:2nd-moment-1} \\
    \frac{1}{3}\nabla\cdot\phi^{(s+1)}+\Sigma_t J^{(s+1)} = \nabla\cdot F^{(s+1/2)}
    \label{eq:2nd-moment-2}
    \shortintertext{where}
    F^{(s+1/2)}_{\alpha\beta} = \int_{4\pi}
    \left(\frac{1}{3}\delta_{\alpha\beta}-\Omega_\alpha\Omega_\beta\right)
    \Psi^{(s+1/2)} d\Omega \label{eq:2nd-moment-3}
  \end{gather}
  %
  The transport subdomains require interface conditions in the form of boundary sources from
  neighboring diffusion subdomains.
\end{frame}

>>>>

  Gol'din originally developed the quasi-diffusion (QD) method as a transport method acceleration
  scheme \cite{goldin_quasi-diffusion_1964}.
  \begin{gather}
    \mbox{\small Zeroth angular moment: } 
    \nabla\cdot J(\vec{r}) + \Sigma_t(\vec{r})\phi(\vec{r}) = \Sigma_{s,0}(\vec{r})\phi(\vec{r}) +
    Q_0(\vec{r}) \label{eq:qd-low-0th} \\
    \mbox{\small First angular moment: }
    \nabla\cdot\left(\vec{\vec{E}}(\vec{r})\phi(\vec{r})\right) + \Sigma_t(\vec{r})J(\vec{r}) =
    \Sigma_{s,1}(\vec{r})J(\vec{r}) + Q_1(\vec{r}) \label{eq:qd-low-1st}
    \shortintertext{\small where}
    \vec{\vec{E}} = \frac{\int_{4\pi}d\hat{\Omega}\ \hat{\Omega}\hat{\Omega}\psi(\vec{r})}{
    \int_{4\pi}d\hat{\Omega}\ \psi(\vec{r})} = \mbox{\small Eddington tensor}.
  \end{gather}
  %
  Gol'din later extended it to a three-level method by deriving effective gray (one-group)
  low-order QD equations \cite{anistratov_solution_1986}.
  \begin{figure}[t]
    \tikzstyle{every node}=[font=\small]
    \centering
    \begin{tikzpicture}
      \node (1) [solver2] {Multigroup high-order transport};
      \node (2) [solver2, right of=1, xshift=3cm] {Multigroup low-order QD};
      \node (3) [solver2, right of=2, xshift=3cm] {Effective low-order transport};
      \draw [arrow] (1.10) -- node[anchor=south, text width=2cm, align=center] {Group\\ Eddington
        and boundary factors} (2.170);
      \draw [arrow] (2.190) -- node[anchor=north, text width=2cm, align=center] {Effective flux
        and precursors} (1.350);
      \draw [arrow] (2.10) -- node[anchor=south, text width=2cm, align=center] {Collapsed Eddington
        and boundary factors} (3.170);
      \draw [arrow] (3.190) -- node[anchor=north, text width=2cm, align=center] {Effective flux
        and precursors} (2.350);
    \end{tikzpicture}
    \caption{Algorithm flowchart for the three-level quasi-diffusion method.}
    \label{fig:algorithm}
  \end{figure}
\end{frame}

@@

  It uses two-level neutronics method based on the Second-Moment method \cite{lewis_comparison_1976}.
  The low-order second-moment equations on the $(s+1)$th iteration are:
  \begin{gather}
    \nabla\cdot J^{(s+1)}+\Sigma_a\phi^{(s+1)} = q, \label{eq:2nd-moment-1} \\
    \frac{1}{3}\nabla\cdot\phi^{(s+1)}+\Sigma_t J^{(s+1)} = \nabla\cdot F^{(s+1/2)}
    \label{eq:2nd-moment-2}
    \shortintertext{where}
    F^{(s+1/2)}_{\alpha\beta} = \int_{4\pi}
    \left(\frac{1}{3}\delta_{\alpha\beta}-\Omega_\alpha\Omega_\beta\right)
    \Psi^{(s+1/2)} d\Omega \label{eq:2nd-moment-3}
  \end{gather}
  %
  The transport subdomains require interface conditions in the form of boundary sources from
  neighboring diffusion subdomains.
\end{frame}
